Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-15 paper/paper.tex
typesetting units
add authors and affiliations
use addaddr

\author{Author names omitted for review}

>>>>

\author{Alessandro Abate$^{1}$, Iury Bessa$^{2}$, Dario Cattaruzza$^{1}$, Lucas Cordeiro$^{1,2}$, \\ 
Cristina David$^{1}$, Pascal Kesseli$^{1}$ and Daniel Kroening$^{1}$
\and
$^{1}$\affaddr{University of Oxford, Oxford, United Kingdom} \\
$^{2}$\affaddr{Federal University of Amazonas, Manaus, Brazil}
}
